Almost compatible functions and infinite length games

### 2015-11-17 articles/almost-compatible-functions-and-topological-games/article.tex
partial revision of kurepa family to S' proof

  \begin{definition}
    The statement \(S(\kappa)\) (given as \(S(\kappa,\aleph_0,\omega)\)
    in \cite{MR1129143}) claims that there exist injections
    \(f_A:A\to\omega\) for each \(A\in[\kappa]^{\leq\aleph_0}\) such that
    the collection \(\{f_A:A\in[\kappa]^{\leq\aleph_0}\}\) is pairwise
    almost compatible.
  \end{definition}

@@

  \begin{definition}
    \(S'(\theta)\) states that there exists a cofinal family
    \(\mc S\subseteq[\theta]^{\omega}\) and a collection of pairwise
    almost compatible
    finite-to-one functions \(\{f_S\in\omega^S:S\in\mc S\}\)
  \end{definition}

  \begin{definition}
    \(S(\theta)\) strengthens \(S'(\theta)\) by requiring the collection
    to contain one-to-one functions.
  \end{definition}

  We wish to show that Scheeper's original \(S(\theta)\) is strictly stronger
  than \(S'(\theta)\).

@@

  \begin{definition}
    A Kurepa family \(\mc K\subseteq[\theta]^{\omega}\) on \(\theta\)
    satisfies that
    \(\mc K\rest A=\{K\cap A:K\in\mc K\}\) is countable
    for each \(A\in[\theta]^\omega\).
  \end{definition}

@@

  \begin{theorem}
    \(S'(\theta)\) holds whenever there exists a cofinal Kurepa family on \(\theta\).
  \end{theorem}

  \begin{proof}
    Let \(k<\omega\), and \(\mc K=\{K_\alpha:\alpha<\kappa\}\)
    be a cofinal Kurepa family on \(\theta\).
    We should define \(f_\alpha:K_\alpha\to\omega\) for each \(\alpha<\kappa\).

    Suppose we've defined pairwise almost compatible
    \(\{f_\beta:\beta<\alpha\}\). To define
    \(f_\alpha\), we first recall that \(\mc K\rest K_\alpha\) is countable,
    so we may choose \(\beta_n<\alpha\) for \(n<\omega\) such that
    \(
      \{K_\beta:\beta<\alpha\}\rest K_\alpha \setminus \{\emptyset\}
        =
      \{K_\alpha\cap K_{\beta_n}:n<\omega\}
    \).
    Let \(K_\alpha=\{\delta_{i,j}:i\leq\omega,j<w_i\}\) where
    \(w_i\leq\omega\) for each \(i\leq\omega\),
    \(
      K_\alpha\cap \left(K_{\beta_n}\setminus\bigcup_{m<n}K_{\beta_m}\right)
        =
      \{\delta_{n,j}:j<w_n\}
    \),
    and
    \(
      K_\alpha\setminus\bigcup_{n<\omega}K_{\beta_n}
        =
      \{
        \delta_{\omega,j}:j<w_\omega
      \}
    \).
    Then let \(f_\alpha(\delta_{n,j})=\max(n,f_{\beta_n}(\delta_{n,j}))\) for
    \(n<\omega\) and \(f_\alpha(\delta_{\omega,j})=j\) otherwise.

    We should show that \(f_\alpha\) is finite-to-one. Let \(n<\omega\).
    We need only worry about \(\delta_{m,j}\) for \(m\leq n\) since
    \(f_\alpha(\delta_{m,j})\geq m\). Since each
    \(f_{\beta_m}\) is finite-to-one, \(f_{\beta_m}(\delta_{m,j})\leq n\)
    for only finitely many \(j\). Thus \(f_\alpha\) maps to
    \(n\) only finitely often.

    We now want to demonstrate that \(f_\alpha\sim f_{\beta_n}\) for all
    \(n<\omega\). We again need only concern ourselves with \(\delta_{m,j}\) for
    \(m\leq n\) since otherwise \(\delta_{m,j}\not\in K_{\beta_n}\).
    For \(m=n\), we have
    \(f_\alpha(\delta_{n,j})=\max(n,f_{\beta_n}(\delta_{n,j}))\) which differs
    from \(f_{\beta_n}(\delta_{n,j})\) for only the finitely many \(j\) which
    are mapped below \(n\) by \(f_{\beta_n}\).
    For \(m<n\) and \(\delta_{m,j}\in K_{\beta_n}\),we have
    \(f_\alpha(\delta_{m,j})=\max(m,f_{\beta_m}(\delta_{m,j}))\) which can
    only differ
    from \(f_{\beta_n}(\delta_{m,j})\) for only the finitely many \(j\) which
    are mapped below \(m\) by \(f_{\beta_m}\) or the finitely many \(j\)
    for which the
    almost compatible \(f_{\beta_n}\sim f_{\beta_m}\) differ.
  \end{proof}

>>>>

  \begin{definition}
    The statement \(S(\kappa)\) (given as \(S(\kappa,\aleph_0,\omega)\)
    in \cite{MR1129143}) claims that there exist one-to-one functions
    \(f_A:A\to\omega\) for each \(A\in[\kappa]^{\leq\aleph_0}\) such that
    the collection \(\{f_A:A\in[\kappa]^{\leq\aleph_0}\}\) is pairwise
    almost compatible.
  \end{definition}

@@

  \begin{definition}
    The statement \(S'(\kappa)\) weakens \(S(\kappa)\) be only requiring
    the witness functions \(f_A:A\to\omega\) to be finite-to-one.
  \end{definition}

  The following observation will be convenient.

  \begin{proposition}
    \(S(\kappa)\) and \(S'(\kappa)\) need only be witnessed by
    functions \(\{f_A:A\in\mc S\}\) for some family \(\mc S\)
    cofinal in \([\kappa]^{\leq\aleph_0}\).
  \end{proposition}

  \begin{proof}
    For each \(A\in[\kappa]^{\leq\aleph_0}\) choose \(A'\supseteq A\)
    from \(\mc S\) and let \(g_A=f_{A'}\rest A\).
  \end{proof}

  In the next section we will show that \(S'(\kappa)\) is sufficient
  for the applications to the Scheepers and Menger games.
  In the meantime, we will demonstrate that \(S'(\kappa)\) is strictly
  weaker than \(S(\kappa)\).

  Recall the following.

  \begin{definition}
    A Kurepa family \(\mc K\subseteq[\kappa]^{\aleph_0}\) on \(\kappa\)
    satisfies that
    \(\mc K\rest A=\{K\cap A:K\in\mc K\}\) is countable
    for each \(A\in[\kappa]^{\aleph_0}\).
  \end{definition}

  \begin{theorem}
    \(S'(\kappa)\) holds whenever there exists a cofinal Kurepa family on \(\kappa\).
  \end{theorem}

  \begin{proof}
    Let \(\mc K=\{K_\alpha:\alpha<\theta\}\)
    be a cofinal Kurepa family on \(\kappa\).
    We first define \(f_\alpha:K_\alpha\to\omega\) for each \(\alpha<\theta\).

    Suppose we've already defined pairwise almost compatible finite-to-one functions
    \(\{f_\beta:\beta<\alpha\}\). To define
    \(f_\alpha\), we first recall that \(\mc K\rest K_\alpha\) is countable,
    so we may choose \(\beta_n<\alpha\) for \(n<\omega\) such that
    \(
      \{K_\beta:\beta<\alpha\}\rest K_\alpha \setminus \{\emptyset\}
        =
      \{K_\alpha\cap K_{\beta_n}:n<\omega\}
    \).
    Let \(K_\alpha=\{\delta_{i,j}:i\leq\omega,j<w_i\}\) where
    \(w_i\leq\omega\) for each \(i\leq\omega\),
    \(
      K_\alpha\cap \left(K_{\beta_n}\setminus\bigcup_{m<n}K_{\beta_m}\right)
        =
      \{\delta_{n,j}:j<w_n\}
    \),
    and
    \(
      K_\alpha\setminus\bigcup_{n<\omega}K_{\beta_n}
        =
      \{
        \delta_{\omega,j}:j<w_\omega
      \}
    \).
    Then let \(f_\alpha(\delta_{n,j})=\max(n,f_{\beta_n}(\delta_{n,j}))\) for
    \(n<\omega\) and \(f_\alpha(\delta_{\omega,j})=j\) otherwise.

    We should show that \(f_\alpha\) is finite-to-one. Let \(n<\omega\).
    Since \(f_\alpha(\delta_{m,j})\geq m\), we only consider the finite cases
    where \(m\leq n\). Since each
    \(f_{\beta_m}\) is finite-to-one, \(f_{\beta_m}(\delta_{m,j})\leq n\)
    for only finitely many \(j\). Thus
    \(f_\alpha(\delta_{m,j})=\max(m,f_{\beta_m}(\delta_{m,j}))\) maps to
    \(n\) for only finitely many \(j\).

    %TODO proof
    We now want to demonstrate that \(f_\alpha\sim f_{\beta_n}\) for all
    \(n<\omega\). We again need only concern ourselves with \(\delta_{m,j}\) for
    \(m\leq n\) since otherwise \(\delta_{m,j}\not\in K_{\beta_n}\).
    For \(m=n\), we have
    \(f_\alpha(\delta_{n,j})=\max(n,f_{\beta_n}(\delta_{n,j}))\) which differs
    from \(f_{\beta_n}(\delta_{n,j})\) for only the finitely many \(j\) which
    are mapped below \(n\) by \(f_{\beta_n}\).
    For \(m<n\) and \(\delta_{m,j}\in K_{\beta_n}\),we have
    \(f_\alpha(\delta_{m,j})=\max(m,f_{\beta_m}(\delta_{m,j}))\) which can
    only differ
    from \(f_{\beta_n}(\delta_{m,j})\) for only the finitely many \(j\) which
    are mapped below \(m\) by \(f_{\beta_m}\) or the finitely many \(j\)
    for which the
    almost compatible \(f_{\beta_n}\sim f_{\beta_m}\) differ.
  \end{proof}

  \newpage

  \section{TODO ALL THIS STUFF NEEDS EDITING STILL}

@@

@@
